Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-10 paper/sec-pileup.tex
more work on paper

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/ssb_pu.pdf}
\includegraphics[width=0.48\textwidth]{plots/sb_pu.pdf}
\caption{\small
  Same as Fig.~\ref{fig:sb_mva} this time for the analysis including
  effects of PU, with $\la n_{\rm PU}\ra=150$.
}
\label{fig:sb_mva_pu}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

In Fig.~\ref{fig:sb_mva_pu} we show the signal significance,
$S/\sqrt{B}$, as well as the signal over background ratio,
$S/B$, as a function of the NN discriminant, in the case
of the analysis including the effects of PU
with $\la n_{\rm PU}\ra=150$.
%
The corresponding results in the case without PU were shown in
Fig.~\ref{fig:sb_mva}.
%
As can be seen, the MVA-driven enhancement is robust event in the
presence of PU, and a total signal significance of
almost $S/\sqrt{B}\simeq 3$ is also obtained in this case.
%
Therefore, we conclude that the qualitative results obtained
in the previous section are robust even in the presence
of realistic PU effects.
%
Note that no specific effort has been performed to
optimize PU subtraction (for example by tuning the value
of the patch length $a$ in {\tt SoftKiller}), so there is
certainly still room for improvement.
